A thesis draft

### 2018-10-16 res/sections/07-Introduction.tex
Add content to intro and created background empty file

 Through the history of internet, many factors changed and new innovations came,
 but at the end of the day a foundamental key remained: connection performances
 are, indeed, what the users really want.\todo{Idea: talk about how TCP/IP
   performes quite well in wired connections, while in wireless one, such as
   wireless/satellite, sucks ass} In this context network optimization plays an
 important role, and it is for this reason that network packets are elaborated,
 compressed and processed while traversing the network in order to make their
 transmission as fast as possible. On top of that, mobile traffic is
 continuously surging every year, with the backbones having more and more data
 to deliver, making in-hardware backbone solutions less efficent. Their
 time-to-deploy, in fact, is very high compared to the requirements of the
 network. With this trend, in-hardware solutions will not be able to keep up. Is
 with this considerations that software a software approach is being proposed to
 become the new way to deploy network components. While less efficent, they are
 faster to bring them up, offering an unprecedented flexibility\todo{CITE:
   SDN/NFV-Based Mobile Packet Core Network Architectures: A Survey}.
 Furthermore, new virtualization technologies such as Cloud computing and Docker
 are becoming more and more mature for being employed in large-scale production
 environments, where new frameworks, called orchestrators (e.g. Kubernetes,
 Docker Swarm), allow to easily manage the application lifecyle, i.e.
 deployment, scale up/down and finally, removal.

>>>>

 Through the history of internet, many factors changed and new innovations came,
 but at the end of the day a foundamental key remained: connection performances
 are, indeed, what the users really want.\todo{Idea: talk about how TCP/IP
   performes quite well in wired connections, while in wireless one, such as
   wireless/satellite, sucks ass}
With the arrival of mobile connectivity, wireless networks started to have an 
important role in everyone's life. In this context network efficiency plays 
an important role with the development of new connectivity standards (e.g 2G, 
3G, LTE) and the creation of common communication protocols ad-hoc versions 
(i.e. TCP versions specialized for exploit the characteristic of wireless 
networks). It is for this reason that, beside improved radio communications, 
backend infrastructure began to be refined too. During their travel to the 
destination packets are elaborated, compressed and processed in order to make 
their transmission as fast as possible.
On top of that, mobile traffic is continuously surging every year, with the 
backbones having more and more data to deliver, making in-hardware backbone 
solutions less efficent. Their time-to-deploy, in fact, is very high compared 
to the requirements of the network. With this trend, in-hardware solutions 
will not be able to keep up. Is with this considerations that software a 
software approach is being proposed to become the new way to deploy network 
components. While less efficent, they are faster to bring them up, offering an 
unprecedented flexibility\todo{CITE: SDN/NFV-Based Mobile Packet Core Network 
Architectures: A Survey}.
 Furthermore, new virtualization technologies such as Cloud computing and Docker
 are becoming more and more mature for being employed in large-scale production
 environments, where new frameworks, called orchestrators (e.g. Kubernetes,
 Docker Swarm), allow to easily manage the application lifecyle, i.e.
 deployment, scale up/down and finally, removal.
